Data Preparation, Integration and Cleaning

### 2017-02-18 abbDataPrep_Script.Rmd
Fixed order of $500 cut

Next we extract all of the daily reservation data that fits our criteria -- reserved and not over $500 per night^[Note that there are some outlying daily observations that do not agree with the property level Airbnb summary data from the data source.  We do this step to remove those]. From this information we calculate the median nightly reservation price for each property and append it to the property level data.

@@

  # Get all of the reservations
  resv.daily <- daily.data[daily.data$status == 'R' &
                              daily.data$price < 500, ]

@@

```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 ## Filter the short term data

>>>>

Next we extract all of the daily reservation data for the reserved nightly. From this information we calculate the median nightly reservation price for each property and append it to the property level data.

@@

   # Get all of the reservations
  resv.daily <- daily.data[daily.data$status == 'R', ]

@@

```{r ltprice_fltr33s, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
